Schema Change: Challenge Problems

### 2024-05-23 paper.tex
combo diagram

\begin{figure}

  \begin{tikzcd}[sep = huge]
    schema_1  \arrow[r, "constrains"] \arrow[d, "change"{left},""{name=L}]& data_1 \arrow[d, ""{name=R, left}, "migration"{right}] \\
    schema_2 \arrow[r, "constrains"{below}] & data_2
    \arrow[Rightarrow, from=L, to=R, "propagate"]
  \end{tikzcd}

  \begin{tikzcd}[sep = huge]
    schema_1  \arrow[r, "constrains"] \arrow[d, "change"{left},""{name=L}]& code_1 \arrow[d, ""{name=R, left}, "refactor"{right}] \\
    schema_2 \arrow[r, "constrains"{below}] & code_2
    \arrow[Rightarrow, from=L, to=R, "propagate"]
  \end{tikzcd}

  \caption{Commutative diagrams.}
  \label{fig:diagrams}
\end{figure}

>>>>

  \begin{tikzcd}[sep = huge]
    \textsf{code}_1
    \arrow[d, "\textsf{refactor}"{left},""{name=L}]
    &
    \textsf{schema}_1
    \arrow[l, "\textsf{constrains}"{above}]
    \arrow[r, "\textsf{constrains}"]
    \arrow[d, red, "\textsf{change}"{near start, description}, ""{name=CL, left}, ""{name=CR}]
    &
    \textsf{data}_1
    \arrow[d, ""{name=R, left}, "\textsf{migrate}"{right}]
    \\
    \textsf{code}_2
    &
    \textsf{schema}_2
    \arrow[l, "\textsf{constrains}"{below}]
    \arrow[r, "\textsf{constrains}"{below}] &
    \textsf{data}_2
    \arrow[Rightarrow, from=CL, to=L, "\textsf{propagate}"{below}]
    \arrow[Rightarrow, from=CR, to=R, "\textsf{propagate}"{below}]
  \end{tikzcd}
